Calculating Entropies With Nested Sampling

### 2017-01-14 paper/ms.tex
Wrote down the Shannon entropy and the product rule

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2016}
%\externaleditor{Academic Editor: xx}
\history{Received: xx / Accepted: xx / Published: xx}

@@

\DeclareUnicodeCharacter{00A0}{ }
\newcommand{\xx}{\boldsymbol{\theta}}
\newcommand{\dx}{d\boldsymbol{\theta}}
\newcommand{\data}{\boldsymbol{D}}
\newcommand{\II}{\boldsymbol{I}}

@@

>>>>

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{}       %\doinum{10.3390/------}
\pubvolume{}    % \pubvolume{xx}
\pubyear{2017}
%\externaleditor{Academic Editor: xx}
\history{In preparation}%\history{Received: xx / Accepted: xx / Published: xx}

@@

\DeclareUnicodeCharacter{00A0}{ }
\newcommand{\x}{\boldsymbol{x}}
\renewcommand{\d}{\boldsymbol{d}}

@@

If an unknown quantity $\x$ has a discrete probability distribution $p(\x)$,
the entropy is
\begin{align}
H_{\x} &= -\sum_{\x} p(\x) \log p(\x)
\end{align}
where the sum is over all of the possible values of $\x$ under consideration.
This probability distribution is implicitly conditional on some prior
information, which is have omitted from the notation.

\section{Entropies in Bayesian inference}

In a standard situation where Bayesian inference would be used,
the unknown quantities are the parameters $\x$ and the data $\d$
(which subsequently becomes known). The prior information leads the
user to specify a prior distribution $p(\x)$ for the unknown parameters,
along with a ``sampling distribution'' $p(\d | \x)$ describing prior knowledge
of how the data is related to the parameters. By the product rule, this yields
a joint prior
\begin{align}
p(\x, \d) &= p(\x)p(\d | \x)
\end{align}
